Competing Bandits: The Perils of Exploration under Competition

### 2018-09-05 paper/content/model.tex
add timing results

We fix the sliding window size $M = 100$. We found that lower values induced too much random noise in the results, and increasing $M$ further did not make a qualitative difference. Unless otherwise noted, \asedit{we used $T = 2000$}.

The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 \asedit{XX-Hz} CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about \asedit{XX} hours.

>>>>

We fix the sliding window size $M = 100$. We found that lower values induced too much random noise in the results, and increasing $M$ further did not make a qualitative difference. Unless otherwise noted, we used $T = 2000$.

The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 2200Hz CPU cores, with 8 GB RAM per core. With this implementation, each experiment took about 10.5 hours.
